Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-30 thesis/acm/paper.tex
first page latex stuff
Added category, first page

\conferenceinfo{14th International Workshop on Principles of Software Evolution}{2015 Bergamo, Italy}

\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}
\subtitle{[Extended Abstract]
}

@@

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory, Design or Verification maybe?}

>>>>

\conferenceinfo{14th IWPSE} {'15 Bergamo, Italy}
\CopyrightYear{2015}

\crdata{1-23456-78-9/01/23}

\title{Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective}

@@

\category{K.6.3}{Software Engineering}{Distribution, Maintenance, Enhancement}[Restructuring, reverse engineering, and reengineering]

\terms{Theory, Design or Verification/Documentation maybe?}
